# create datasets

from parsed ygoprodeck csv files clump them together


tournaments column as:
id, name, country, event-date, winner, format, slug, player_count, is_approximate_player_count
```{r}
TOURNAMENTS_FOLDER = "tournaments-TCG-3/"
TOURNAMENTS_FILENAME = "tournaments-TCG-3-six_months.csv"
CSV_PARSED_FOLDER = "./parsed/"

TOURNAMENTS = read.csv(paste(CSV_PARSED_FOLDER, TOURNAMENTS_FILENAME, sep = "")) # READ ONLY
TOURNAMENTS$X = NULL
```

paste all tournaments together, add column for the tournament id
```{r}
TOURNAMENTS_DATASET = data.frame()
for (tournament in TOURNAMENTS$slug) {
    tournament_csv = read.csv(paste(CSV_PARSED_FOLDER, TOURNAMENTS_FOLDER, tournament, ".csv", sep = ""))
    tournament_csv$X = NULL
    tournament_csv["slug"] = tournament
    
    TOURNAMENTS_DATASET = rbind(TOURNAMENTS_DATASET, tournament_csv) # vstack
}
```



# create encoded datasets
maliss -> 0
...
ryzeal -> 3

"DATASET-encoded-archetypes.csv"

```{r}
archetypes = TOURNAMENTS_DATASET$archetype
archetypes = archetypes[!duplicated(archetypes)]
print(archetypes)

archetypes_info = data.frame(
  "archetype" = archetypes,
  "archetype_encoding" = 0:(length(archetypes) - 1),
  "archetype_power_level" = 0
)
```

added column encoding of archetype, its order is lost tho

```{r}
TOURNAMENTS_DATASET = merge(TOURNAMENTS_DATASET, archetypes_info, by = "archetype")
```

```{r}
write.csv(TOURNAMENTS_DATASET, paste("DATASET-", TOURNAMENTS_FILENAME, sep = ""))
write.csv(archetypes_info, "DATASET-archetypes-info.csv")
```


# rank tier of deck (t1,t2) 1...10

"Memento"
"Maliss"
"Ryzeal"
"Bystial"
"Mitsurugi"
"Mermail"
"Crystron"
"Blue-Eyes"
"Snake-Eye"
"Fiendsmith"
"White Forest"
"Yubel"
"Salamangreat"
"Labrynth"
"Odion"
"Rescue-ACE"
"Tenpai Dragon"
"Fire King"
"Phantom Knights"
"Despia"
"Stun"           
"Primite"
"Voiceless Voice"
"Orcust"
"Ritual Beast"
"Chimera"
"Kashtira"
"Centur-Ion"
"Unchained"
"Exodia"
"Dragon Link"
"Floowandereeze"
"Traptrix"

```{r}
DECK_TIERS = read.csv("./datasets/deck_powerlevel.csv", sep = "")
```

# put all deck cards in single dataset
```{r}
library(dplyr)

# Set the path to the directory containing your CSV files
path <- "./parsed/tournaments-TCG-3/decks/"  # replace with your actual path

# Get the list of CSV files in the directory
file_list <- list.files(path, pattern = "\\.csv$", full.names = TRUE)

# Read and merge all CSVs with an additional 'deck_id' column
DECKS_CSV <- lapply(file_list, function(file) {
  df <- read.csv(file)
  df$deck_id <- tools::file_path_sans_ext(basename(file)) # remove ".csv"
  return(df)
}) %>%
  bind_rows()  # Merge all into a single data frame

# View result
head(DECKS_CSV)
```
merge archetype in deck
# DOESNT WORK
```{r}
# Step 1: Keep only one archetype per deck_id (first occurrence)
tournament_archetypes <- TOURNAMENTS_DATASET %>%
  filter(!is.na(deck_id)) %>%
  distinct(deck_id, .keep_all = TRUE) %>%
  dplyr::select(deck_id, archetype)

# Step 2: Join to add archetype to decks
DECKS_CSV <- DECKS_CSV %>%
  left_join(tournament_archetypes, by = "deck_id")

```


```{r}
write.csv(DECKS_CSV, "DATASET-decks-TCG-3-six_months.csv")
```


